The influence of small reservoirs on hydrological drought propagation in space and time

### 2022-10-28 LateX/Feb-3-22-latex-templates/paper_Colombo.tex
submission paper ended

\begin{keypoints}
\item We evaluated how a dense network of small and unmonitored reservoirs (DRN) impacts drought events in time and space
\item Drought cycle analyses and the downstreamness concept were coupled with hydrological modeling-based DRN scenarios to assess the impacts in time and space, respectively
\item The presence of small reservoirs accelerated the transition towards hydrological droughts by 20\% on average and slowed down drought recovery by 25\%, while shifting upstream water storage capacity distribution in space by 8\%
\end{keypoints}

@@

\section*{Plain Language Summary}
Human impacts have been found in a broad spectrum of environmental processes and phenomena. Droughts make no exception. Droughts, as periods of exceptional lack of water, are one of the disasters that produce the most intense environmental and socio-economic impacts. One of the most common strategies for reducing drought-related impacts is the construction of small reservoirs to store water. This practice can generate a false sense of water security and increase water demand, which in turn results in more reservoirs being constructed. When the presence of these reservoirs becomes diffused and in high numbers, it may enhance the persistence of droughts, making them longer and more intense. Since these effects are still unclear, we modeled multiple scenarios representing a North-East Brazilian river basin with and without small reservoirs. Through two methods (the Drought Cycle Analysis and the Downstreamness analysis), these scenarios were analyzed to assess the reservoirs’ effects in time and space. We found that in the region drought events last on average 12\% longer due to the small reservoirs’ presence. This is linked to the accelerated transition from meteorological to hydrological drought (+20\%) and the slowdown of the large reservoirs’ recovery from a drought condition (-25\%). We found that the overall storage distribution is shifted upstream by 8\% on average, but when both large and small reservoirs are present the stored volume distribution behavior is not straightforward. The findings confirm the need to consider small reservoirs when addressing drought management policies.

@@

\subsubsection{Small reservoirs representation}
The modeling approach to the reservoirs needs to classify them into strategic and small reservoirs, according to location and size \cite{Guntner2004}. The strategic reservoirs listed in Table~\ref{tab1} are individually parameterized in WASA-SED, also providing their daily regulated discharge time series. Their water balance is calculated explicitly and individually for each reservoir. Due to the uncontrolled and unmonitored nature of small reservoirs composing the DRN, not enough information is available concerning dam building, location, size and water use. They are grouped into 5 storage capacity classes and the water balance is computed for a hypothetical reservoir with mean characteristics, representative of each class and sub-basin. The water storage volume is then given by the product of the water storage of the representative reservoir by the total number of reservoirs from that class within a sub-basin. The generated runoff of the sub-basin is distributed among the reservoir classes through a cascade routing scheme starting from the lowest class to the highest, using a weighting factor computed as a ratio between the runoff contributing area of that reservoir class and the sub-basin area \cite{Mamede2018}. A detailed description of the calculation of water fluxes through the classes of reservoirs can be found in \citeA{Mamede2008}, while equations and other information about the hydrological and reservoir module can be found in \citeA{Guntner2002}.

@@

\newpage
\appendix
\section{Additional table}

%Table A
\begin{table}
 \caption{Appendix: List of centralized reservoirs, with storage capacity and upstream catchment. The table is ordered by decreasing storage capacity. Information retrieved from FUNCEME database \url{funceme.br/hidro-ce-zend/}.}\label{tabA}
 \centering
 \begin{tabular}{c c c c}
 \hline
  Name  & Year constructed & Storage capacity & Drainage area\\
  & & [$Hm^3$] & [$km^2$]\\
 \hline
Arrojado Lisboa 	& 1966 &	 14,221	& 1600\\
Pedras Brancas	& 1978	& 1,937 &	434\\
Cedro			& 1906	& 206 &	126\\
Fogareiro 		& 1996	 & 5,111 & 	119\\
Cipoada			& 1992	& 351 &	86.1\\
Pirabibu			& 2000	& 503	& 74\\
Patu	 			& 1988	& 995	& 71.8\\
Poço do Barro	& 1956	 & 374 & 52\\
Serafim Dias 	& 1995 &	1,630 &	43\\
Umari			& 2011	& 975	& 30\\
Sao Jose II		& 1992	& 185	& 29.1\\
Vieirão			& 1988	& 400 &	21\\
Trapiá II 		& 1992 & 	129 &	18.2\\
Curral Velho	 	& 2007 & 	79 & 	12.2\\
Monsenhor Tabosa & 1998 & 77 &	12.1\\
Quixeramobim 	& 1966 & 7,021 &	7.88\\
Sao José I		& 1988 & 	188 & 	767\\
Capitão Mor		& 1988	& 110 &	6\\
Jatobá 			& 1997 &	40	& 1.07\\
 \hline
 \end{tabular}
\end{table}

>>>>

\begin{keypoints}
\item We evaluated how a dense network of small and unmonitored reservoirs (DRN) impacts drought events in time and space
\item Drought cycle and downstreamness analyses were coupled with hydrological modeling based DRN scenarios to assess impacts in time and space
\item The DRN accelerated the transition towards hydrological droughts and slowed down drought recovery, while storage capacity was moved upstream
\end{keypoints}

@@

\section*{Plain Language Summary}
Human impacts have been found in a broad spectrum of environmental processes and phenomena. Droughts make no exception. Droughts, as periods of exceptional lack of water, are one of the disasters that produce the most intense environmental and socio-economic impacts. One of the most common strategies for reducing drought-related impacts is the construction of small reservoirs to store water. When these reservoirs are diffused and in high numbers, their presence may increase droughts intensity and length. Since these effects are still unclear, we modeled multiple scenarios representing a North-East Brazilian river basin with and without small reservoirs. These scenarios were analyzed through two methods to assess the reservoirs’ effects in time and space. We found that drought events last on average 12\% longer due to the small reservoirs’ presence in the region. This is linked to the accelerated transition from meteorological to hydrological drought (+20\%) and the slowdown of the large reservoirs’ recovery from a drought condition (-25\%). The overall storage distribution is shifted upstream by 8\% on average, but when both large and small reservoirs are present the stored volume distribution behavior is not straightforward. The findings confirm the need to consider small reservoirs when addressing drought management policies.

@@

\subsubsection{Small reservoirs representation}
The modeling approach to the reservoirs needs to classify them into strategic and small reservoirs, according to location and size \cite{Guntner2004}. The strategic reservoirs (listed in Supporting Information) are individually parameterized in WASA-SED, also providing their daily regulated discharge time series. Their water balance is calculated explicitly and individually for each reservoir. Due to the uncontrolled and unmonitored nature of small reservoirs composing the DRN, not enough information is available concerning dam building, location, size and water use. They are grouped into 5 storage capacity classes and the water balance is computed for a hypothetical reservoir with mean characteristics, representative of each class and sub-basin. The water storage volume is then given by the product of the water storage of the representative reservoir by the total number of reservoirs from that class within a sub-basin. The generated runoff of the sub-basin is distributed among the reservoir classes through a cascade routing scheme starting from the lowest class to the highest, using a weighting factor computed as a ratio between the runoff contributing area of that reservoir class and the sub-basin area \cite{Mamede2018}. A detailed description of the calculation of water fluxes through the classes of reservoirs can be found in \citeA{Mamede2008}, while equations and other information about the hydrological and reservoir module can be found in \citeA{Guntner2002}.

@@

%\newpage
